---
title: "Project Example Data Proposal"
author: "Nathan hogg"
date: "2024-03-18"
output: html_document
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

### **Deadline: April 28, 2024**

### Project Proposal
I have chosen to base my project around a dataset titled "Fraudulent E-Commerce Transactions."
It can be found at https://www.kaggle.com/datasets/shriyashjagtap/fraudulent-e-commerce-transactions
I will be investigating factors that contribute to fraudulent transactions, such as user age, payment method, product type,
 and account age. I will likely strip some of the variables that are unnecessary, such as 
location, device used, and ip address as they don't have much bearing on the analysis.

### Note
All of the data is synthetic.

### Questions of Interest
What factors lead to fraudulent transactions? Are younger people more likely to 
be scammed than older people? Is there a certain type of item that is frequently
fraudulently sold? Are certain payment methods more fraud-resistant? Does price matter, 
or are larger purchases scams as frequently as smaller ones?

### Potential Complications
I think that certain factors could conflict and not always be a sign of fraud.
For example, on certain types of items, old people may experience fraud as much 
as young people, or vice versa. This will have to be investigated.




### Data


```{r}
library(tidyverse)
data <- read_csv("Fraudulent_E-Commerce_Transaction_Data.csv")
head(data)


```

